---
title: "Ligands analysis"
author: "frontallobotomy77"
date: "`r format(Sys.time(), '%d %b %Y')`"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: true
    number_sections: true
    theme: spacelab
    highlight: espresso
    df_print: paged
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Summary <!-- na koniec -->

#Data analysis
##Libraries used in report <!-- opis + kod załączający -->
 - dplyr
 - ggplot2
 - DT
 
```{r libraries initialization, include=FALSE}
if (!require('dplyr')){ 
  install.packages('dplyr')}
library(dplyr)

if (!require('ggplot2')){ 
  install.packages('ggplot2')}
library(ggplot2)

if (!require('DT')){ 
  install.packages('DT')}
library(DT)
```
 

##Initialization <!-- zapewnienie powtarzalności wykonania -->

```{r initialization, include=FALSE}
set.seed(7)
prettyTable <- function(table_df, round_columns=numeric(), round_digits=2) {
    DT::datatable(table_df, style="bootstrap", filter = "top", rownames = FALSE, extensions = "Buttons", options = list(dom = 'Bfrtip',                    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) %>%
    formatRound(round_columns, round_digits)
}
```

#Data loading

```{r data loading, cache=TRUE}
# Start the clock!
ptm <- proc.time()

sample <- read.table(file='data/all_summary.csv', header = TRUE, sep = ';', stringsAsFactors = FALSE, 
                     comment.char = "", strip.white = TRUE, na.strings = 'NA')

# Stop the clock
proc.time() - ptm
```


#Data cleansing

#Missing data processing

#Basic data set specification

#Significant classes extracting

#Correlation between variables

#Cardinality of classes

#Atoms and electrons distribution diagram

#Classes with the greatest inconsistency in selected attributes

#Value distribution chart of selected attributes

#Interactive diagram

#Regression

#Classification
